%------------------------
% Resume Template
% Author : Prakhar Shukla
% Github : https://github.com/imprakharshukla
% License : MIT
%------------------------

\documentclass[a4paper,10pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage{fancyhdr}
\usepackage{xcolor}
\usepackage[pdftex,
            colorlinks = true,
            linkcolor = blue,
            urlcolor  = blue,
            citecolor = blue,
            anchorcolor = blue]{hyperref}
\newcommand{\MYhref}[3][blue]{\href{#2}{\color{#1}{#3}}}%

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.530in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.45in}
\addtolength{\textheight}{1in}

\urlstyle{rm}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-10pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-6pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeItemWithoutTitle}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{#3} & \textit{#4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-3pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-----------------------------
%%%%%%  CV STARTS HERE  %%%%%%

\begin{document}

%----------HEADING-----------------
\begin{center}
  \textbf{{\LARGE Prakhar Shukla}} \\
  \vspace{2pt}
  \href{https://prakhar.codes}{Portfolio: prakhar.codes} $|$ \href{https://github.com/imprakharshukla}{Github: github.com/imprakharshukla} $|$ \href{https://linkedin.com/in/iamprakharshukla}{LinkedIn: linkedin.com/in/iamprakharshukla}
\end{center}

%-----------SUMMARY-----------------
\section{Summary}
\vspace{2pt}
Full-stack software engineer with 4+ years of experience building production systems from zero to scale, across TypeScript, React, Node.js, and AI/LLM-based products. Built Andronix (2.4M+ downloads, \$140K revenue) and led AI agent development at Yobr. \textbf{GitHub: 3,100+ stars · 1000+ forks}

%-----------EXPERIENCE-----------------
\section{Experience}
\resumeSubHeadingListStart
\resumeSubheading
{Founding Software Engineer - Yobr (yobr.io)}{{Oslo, Norway}}
{Full-Time}{May 2025 - Dec 2025}
\resumeItemListStart
\resumeItem{\textbf{Flagship Job Planner}}
{Designed and built flagship Job Planner with nested AI-powered steps and streaming capabilities, reducing job creation time by \textbf{90\%}.}
\resumeItem{\textbf{Tech Stack Migration}}
{Led comprehensive migration to modern architecture using \textbf{\textit{Next.js, Fastify, BullMQ}}, and \textbf{\textit{Trigger.dev}} for async job orchestration. Implemented end-to-end type safety with \textbf{\textit{tRPC}} for shared RPC contracts between frontend and backend.}
\resumeItem{\textbf{AI Agent Development}}
{Architected and deployed sophisticated AI agents with \textbf{100+ tools} using \textbf{\textit{Vercel AI SDK}} and \textbf{\textit{Mastra.ai}}, significantly enhancing the job posting workflow and user experience.}
\resumeItem{\textbf{Event-Driven Notifications}}
{Built event-driven notification system using \textbf{\textit{BullMQ}}, replacing manual email workflows and reducing multi-party interaction turnaround time by \textbf{65\%}.}
\resumeItem{\textbf{DevOps \& Database Architecture}}
{Executed production database migration to \textbf{\textit{PostgreSQL}}. Engineered custom application-layer \textbf{\textit{Row Level Security (RLS)}} alternative, improving performance and maintainability.}
\resumeItem{\textbf{Tech Stack}}
{\textit{Next.js, Fastify, Trigger.dev, tRPC, PostgreSQL, Vercel AI SDK, Mastra.ai, BullMQ}}
\resumeItemListEnd
\vspace{8pt}
\resumeSubheading
{Software Engineering Intern - Yobr (yobr.io)}{{Oslo, Norway}}
{Internship}{Mar 2025 - Apr 2025}
\resumeItemListStart
\resumeItem{\textbf{Flagship Job Planner}}
{Designed flagship Job Planner with nested AI-powered steps and streaming capabilities, enhancing workflow efficiency.}
\resumeItem{\textbf{Organizations \& Team Management}}
{Architected organizations and team management system with \textbf{\textit{Row Level Security}} for secure multi-tenant access.}
\resumeItemListEnd
\vspace{8pt}
\resumeSubheading
{Software Engineering Intern - CaseCraft (NUS Singapore)}{{Singapore}}
{Full-Stack Development \& AI Integration}{Jul 2024 - Nov 2024}
\resumeItemListStart
\resumeItem{\textbf{Full-Stack Development}}
{Engineered frontend using \textbf{\textit{React, Tanstack Router, TailwindCSS}} and backend with \textbf{\textit{TypeScript, ts-rest, PostgreSQL}} achieving end-to-end type safety.}
\resumeItem{\textbf{TypeScript Migration}}
{Led JavaScript to TypeScript migration, resulting in \textbf{24\% reduction} in application failure and error rates.}
\resumeItem{\textbf{AI Integration}}
{Designed and implemented AI pipelines leveraging \textbf{\textit{OpenAI}}, enhancing application capabilities and user engagement.}
\resumeItem{\textbf{Tech Stack}}
{\textit{React, Tanstack Router, TailwindCSS, TypeScript, ts-rest, PostgreSQL, Zod, OpenAI}}
\resumeItemListEnd
\vspace{8pt}
\resumeSubheading
{Founder \& Software Engineer (Product) - Lumoflo}{\MYhref[blue]{https://lumoflo.com}{Website}}
{Full-Stack Multi-Tenant E-commerce Platform. \textbf{\$1.5M+ in transactions processed}}{Apr 2024 - Dec 2024}
\resumeItemListStart
\resumeItem{\textbf{Backend Architecture}}
{Engineered robust backend using \textbf{\textit{Express.js}} and \textbf{\textit{ts-rest}} with end-to-end type safety. Designed \textbf{\textit{monorepo structure}}, reducing build times by \textbf{56\%}.}
\resumeItem{\textbf{Advanced Features}}
{Developed complex account synchronization for carts and queues. Implemented high-performance job queuing system using \textbf{\textit{BullMQ}} and \textbf{\textit{Redis}} for efficient task processing.}
\resumeItem{\textbf{Frontend \& Testing}}
{Led frontend development with \textbf{\textit{Next.js}}, creating a centralized design library. Wrote \textbf{40+ end-to-end tests} for core modules, significantly enhancing deployment confidence.}
\resumeItem{\textbf{Tech Stack}}
{\textit{Express.js, TypeScript, Postgres, Redis, Next.js 14, TailwindCSS, Docker, Jest}}
\resumeItemListEnd
\vspace{8pt}
\resumeSubheading
{Founder \& Software Engineer (Product) - Andronix}{\MYhref{https://andronix.app}{\underline{Website}}}
{\textbf{Ranks No. 1 on Google Play Store for "Linux". 2.4M+ downloads, \$140K+ revenue}}{Apr 2019 - Jun 2024}
\resumeItemListStart
\resumeItem{\textbf{Android App}}
{Developed the entire Android App using \textbf{\textit{Kotlin}} with \textbf{\textit{MVVM architecture}}, handling REST API calls and async operations.}
\resumeItem{\textbf{Backend Architecture}}
{Refactored codebase to \textbf{\textit{TypeScript}}, increased test coverage to \textbf{80\%}, and modularized into microservices for improved scalability and maintenance.}
\resumeItem{\textbf{Tech Stack}}
{\textit{Kotlin, TypeScript, Firebase, Jest}}
\resumeItemListEnd
\resumeSubHeadingListEnd

%-----------SKILLS SUMMARY-----------------
\section{Skills Summary}
  \resumeSubHeadingListStart
    \resumeSubItem{Languages}{TypeScript, JavaScript, SQL, Kotlin, Python, Go, Java, C++}
    \resumeSubItem{Frameworks}{React, Next.js, Express.js, Fastify, React Native, Vue.js}
    \resumeSubItem{Backend \& Infra}{PostgreSQL, Redis, Docker, BullMQ, Firebase}
    \resumeSubItem{AI \& LLMs}{OpenAI, Vercel AI SDK, Mastra.ai, LangChain, LangGraph}
    \resumeSubItem{Testing \& Tooling}{Jest, Cypress, Git}
  \resumeSubHeadingListEnd

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Galgotias College Of Engineering and Technology}{Noida, India}
      {B.Tech in Computer Science and Artificial Intelligence; GPA: 8.3}{2021 - 2025}
  \resumeSubHeadingListEnd

\end{document}
